\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-05-02 project-writings/paper.tex
talk about strict v1 < v2 comparisons

Thus we developed a quite simple and in practice efficient algorithm to
add $\beta$ nodes to an SSA source program by taking
advantage of data structures common to modern SSA based compilers
\footnote{The method for removing $\beta$ nodes is so trivial that we
  could not claim with a straight face that we ``developed an
  algorithm'' to perform it.} .  Pseudocode for the algorithm is shown
in Listing \ref{lst:add_betas}. The algorithm traverses the control
flow group, looking for blocks that have been entered by a jump
conditioned on a relational operation. When we find a variable being
compared to a constant, we compute a range and use it to create a new
$\beta$ node. We want to propagate this range information to all uses
of the variable where the branch is guaranteed to have been taken;
this is accomplished by replacing all uses of original instruction
that are dominated by the new $\beta$ instruction with the $\beta$. To
do this, we take advantage of IonMonkey's use chains to efficiently
iterate over all uses of an instruction.

>>>>

Thus we developed a quite simple and in practice efficient algorithm to
add $\beta$ nodes to an SSA source program by taking
advantage of data structures common to modern SSA based compilers
\footnote{The method for removing $\beta$ nodes is so trivial that we
  could not claim with a straight face that we ``developed an
  algorithm'' to perform it.} .  Pseudocode for the algorithm is shown
in Listing \ref{lst:add_betas}. The algorithm traverses the control
flow group, looking for blocks that have been entered by a jump
conditioned on a relational operation. When we find a variable being
compared to a constant, we compute a range and use it to create a new
$\beta$ node. As a further optimization, we furthermore insert trivial beta
nodes when we encounter a
strict comparison between two variables--the larger must be at least
$-2^{31}+1$, and the smaller can be at most $2^{31}-2$.

After inserting a $\beta$ node, we then want to propagate this range information to all uses
of the variable where the branch is guaranteed to have been taken;
this is accomplished by replacing all uses of original instruction
that are dominated by the new $\beta$ instruction with the $\beta$. To
do this, we take advantage of IonMonkey's use chains to efficiently
iterate over all uses of an instruction.
